Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-09-14 awipev-CO2.Rmd

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d_all %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))
 diff <- d_all %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))

>>>>

Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have been flaged "3" by the SNAPO. After a close look, these samples are not differents from their duplicates. Then we put the flag to "2" (good result).

For TA and CT, samples's flags that have been changed from 3 to 2 are: 2019-12-27 (2264 and 2130), 2019-10-25 (2332 and 2152), 2019-09-06 (2268 and 2116).

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))
